A Large-Scale Study of the Use of Eval in R

### 2020-08-24 inst/paper/main.tex
minor

We have selected \CorpusPackages packages consisting of \CorpusRCodeRnd
lines of R code and \CorpusNativeCodeRnd lines of native code
(C/C++/Fortran).  Figure~\ref{fig:corpus} shows these packages, the size of
the dots reflects the project's size in lines of code including both R and
native code\footnote{Lines of source code reported excludes comments and
  blank lines, counted by \emph{cloc}, \cf
  \url{https://github.com/AlDanial/cloc}}, the x-axis indicates the
expression code coverage in percents and the y-axis gives the number of
reverse dependencies in log scale. Dotted lines indicate means. Large and
popular packages are annotated.

@@

This section presents an overiew of the usage of \eval in our corpus.
Previous work reported that 82\% of JavaScript-enabled web pages used
\eval~\cite{ecoop11}, the case for R is more striking at \miss{100\%} of the
programs use that feature.

This strikingly high number is due to the fact that the language
implementation, the core packages, use \eval extensively. So, in our
analysis, we differentiate \eval based on where they originate from. A {\bf
  core} \eval is one that occurs in the code of a core package.  A {\bf
  dependent} \eval is one that occurs in a package that was included by the
target package. An {\bf own} \eval is one that occurs in the source code of
the target package. We label an \eval occurence as {\bf unknown} when we are
not able to deterimine its origin.\footnote{One source of unknown evals is
  when the \eval function passed as an argument to a higher-order function
  such as \c{lapply}, another is when the code lacks source references.}

Over all, we observed \AllAllCallCountRnd call to \eval in \miss{3,000} runs
of our corpus. The mean number of calls per run was \miss{20} (with a min of
\c{1} and a max of \c{10,000}). Table~\ref{A} details the usage of \eval
across the corpus.  The format is T (m/M/x) where T is the total number of
calls observed for all runs of the corpus, m and x are the minimum and
maximum number of calls for any given run, and A is the mean number of calls
per run.  We can observe \miss{???}. {\bf <The following is a place
  holder. Real text will come once we have the table.>} The majority of
calls come from the core packages.  Kaggle does not have any own calls, any
\eval in those happens in dependent packages and core.

@@

All the \TotalFileCount files in our corpus call eval. \CoreEvalFileCount
(\CoreEvalFilePerc) call only core evals, \AllEvalFileCount (\AllEvalFilePerc)
call both package and core evals; and, \PackageEvalFileCount
(\PackageEvalFilePerc) call only package evals. Of the \AllEvalFileCount
(\AllEvalFilePerc) files that call both package and base eval,
\EightyCoreEvalFilePerc (\EightyCoreEvalFileCount) files make over 80\% eval
calls to core evals.

Of the \missingNumber packages in our corpus, only \missingNumber packages call
eval. \ref{table:top-ten-package-summary} shows the number of calls to eval made
by the ten most frequent callers to eval. These packages together have
\missingNumber callsites and account for \missingPercentage calls to eval.
Furthermore, the top ten callsites account for \missingPercentage of package
eval calls. A single callsite of \TopTenPackageNameA accounts for over
\missingPercentage calls to eval.

>>>>

We have selected \CorpusPackages packages consisting of \CorpusRCodeRnd
lines of R code and \CorpusNativeCodeRnd lines of native code
(C/C++/Fortran).  Figure~\ref{fig:corpus} shows these packages, the size of
the dots reflects the project's size in lines of code including both R and
native code\footnote{Excluding comments and blank lines,
  \url{github.com/AlDanial/cloc}}, the x-axis indicates the expression code
coverage in percents and the y-axis gives the number of reverse dependencies
in log scale. Dotted lines indicate means. Large and popular packages are
annotated.

@@

This section presents an overiew of the usage of \eval in our corpus.
Previous work reported that 82\% of JavaScript-enabled web pages used
\eval~\cite{ecoop11}, the case for R is more striking at \miss{100\%} of the
programs use that feature. In this section, a call to \eval denotes a call
to any one of the functions that provide \eval-like
functionality.\footnote{These include \c{eval}, \c{eval.parent}, \c{evalq}
  and \c{local}.}

This strikingly high number is due to the fact that the language
implementation, the core packages, use \eval extensively. So, in our
analysis, we differentiate \eval based on where they originate from. A {\bf
  core} \eval is one that occurs in the code of a core package.  A {\bf
  dependent} \eval is one that occurs in a package that was included by the
target package. An {\bf own} \eval is one that occurs in the source code of
the target package. We label an \eval occurence as {\bf unknown} when we are
not able to deterimine its origin.\footnote{A source of unknowns is when the
  \eval function is passed as an argument to a function such as \c{lapply},
  another is when the code lacks source references.}

Over all, we observed \AllAllCallCountRnd call to \eval in \miss{3,000} runs
of our corpus. The mean number of calls per run was \miss{20} (with a min of
\miss{1} and a max of \miss{10,000}). Table~\ref{A} details the usage of
\eval across the corpus.  The format is T (m/M/x) where T is the total
number of calls observed for all runs of the corpus, m and x are the minimum
and maximum number of calls for any given run, and A is the mean number of
calls per run.  We can observe \miss{???}. {\bf <The following is a place
  holder. Real text will come once we have the table.>} The majority of
calls come from the core packages.  Kaggle does not have any own calls, any
\eval in those happens in dependent packages and core.  Of the
\missingNumber packages in our corpus, only \missingNumber packages call
eval.

@@

\ref{table:top-ten-package-summary} shows the number of calls to eval
made by the ten most frequent callers to eval. These packages together have
\missingNumber callsites and account for \missingPercentage calls to eval.
Furthermore, the top ten callsites account for \missingPercentage of package
eval calls. A single callsite of \TopTenPackageNameA accounts for over
\missingPercentage calls to eval.
